Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2014-10-23 algorithm.tex
added notes on bounds

Each iteration is called \emph{era}. The $i$-th era is characterized by: 
	\begin{itemize}
	\item the set of regions $\mathcal{R}_{i}$ in which the configuration space
	$mathcal{C}(S)=V_{1}\times\dots\times V_{n}$ is partitioned
	\item an approximation $\mathscr{P}_{i}$ of the Pareto-optimal set.
	\item a set $test_{i}$ of at most $K$ configurations evaluated
	in the era.
	\end{itemize}
$K$ is a parameter that must be set before the algorithm runs.
Note that $\mathcal{R}_{i}$ is a partition of the configuration space, i.e.
	\begin{align}\begin{array}{l}
		\bigcup_{R\in\mathcal{R}_i} R = \mathcal{C}(S) \mbox{ and}\\
		R' \cap R'' = \emptyset, \forall R',R'' \in \mathcal{R}_i
	\end{array}\end{align}

@@

\subsection{Algorithm parameters}
The parameters that completely determine the algorithm are $K$ and $\alpha$.
$K$ corresponds to the population size of the genetic approach. Authors of \cite{zitzler_ec00} found that increasing $k$ not necessarily has a considerable impact on the performance of the algorithm. This holds also in our algorithm.  In addition, while in the genetic approach $K$ must be sufficiently large in order to guarantee diversity of the Pareto set configurations, in our algorithm the diversity is not impacted by $K$ since, by construction, it is guaranteed by the way the configuration space is partitioned, independently from number of configurations evaluated at each iteration. \comment{This is confirmed by the experimental results in \secR{parameter_impact}. }

Parameter $\alpha$ determines when a region is considered of high innovation. High values of $\alpha$ mean that a region will hardly be elected as high-innovation, yielding less splitting operations. This slows down zooming in on portions of configuration space and make the distribution of the simulated configuration more uniform, as there are fewer small regions with a high test configuration concentration. The opposite happens when small values of $\alpha$ are used. \comment{This is confirmed by results of \secR{parameter_impact}. }

>>>>

\comment{TODO AND: c'e' un problema col mathcal, dai un'occhiata qui sotto}
Each iteration is called \emph{era}. The $i$-th era is characterized by: 
	\begin{itemize}
	\item the set of regions $\mathcal{R}_{i}$ in which the configuration space
	$mathcal{C}(S)=V_{1}\times\dots\times V_{n}$ is partitioned
	\item an approximation $\mathscr{P}_{i}$ of the Pareto-optimal set.
	\item a set $test_{i}$ of at most $K$ configurations evaluated
	in the era.
	\end{itemize}
$K$ is a parameter that must be set before the algorithm runs.
Note that $\mathcal{R}_{i}$ is a partition of the configuration space, i.e.
	\begin{align}\begin{array}{l}
		\bigcup_{R\in\mathcal{R}_i} R = \mathcal{C}(S) \mbox{ and}\\
		R' \cap R'' = \emptyset, \forall R',R'' \in \mathcal{R}_i
	\end{array}\end{align}

@@

\subsection{Algorithm Parameters and Scalability} The parameters that
completely determine the algorithm are the configurations budget each
era $K$ and the threshold factor $\alpha$. From a functional point of
view, $K$ is somewhat similar to the population size of a genetic
approach, determining which configuration should be evaluated in the
in the subsequent step of the algorithm. However, as seen in the
previous subsection, the way this $K$ configurations are distributed
across the parameters space is completely different.
Authors of \cite{zitzler_ec00} found that
increasing $k$ not necessarily has a considerable impact on the
performance of the algorithm, and this holds also in our algorithm.
But while in the genetic approach $K$ must be sufficiently large
in order to guarantee diversity of the Pareto set configurations, in
our algorithm the diversity is not impacted by $K$ since, by
construction, it is guaranteed by the way the configuration space is
partitioned, independently from number of configurations evaluated at
each iteration.

On the other side, parameter $\alpha$ determines when a region is considered of high
innovation. High values of $\alpha$ mean that a region will hardly be
elected as high-innovation, yielding less splitting operations. This
slows down zooming in on portions of configuration space and make the
distribution of the simulated configuration more uniform, as there are
fewer small regions with a high test configuration concentration. The
opposite happens when small values of $\alpha$ are used. In this
introductory work we are not explicitly focused on a deep
investigation on how these parameters can be fine tuned, nevertheless
we conducted some preliminary tests to confirm the relative stability
of $PS$ with different choices and to select some ``reasonable'' average
values to perform the design space exploration (see Figure 
\comment{TODO This is confirmed by results of \secR{parameter_impact}
}).

\comment{TODO: Usare notazioni coerenti con le precedenti}
As regards the performance of the proposed approach we can estimate that the
performance of $PS$ is strictly related to the total number of
different configurations evaluated during the exploration. We can
safely make such assumption, because the process of evalutating a new
configuration is the time-dominating one among all the operations
performed. As we will show the
next Section, this is especially true in the hardware/software
design space exploration scenario we are addressing, since benchmark compiling and execution times
are orders of magnitude bigger than the splitting/merging operations and
innovation scores computations.  Ideally, the $i$-th era would provide a new set
$test_i$ of $K$ configurations to be tested. However, we cannot know
a priori how many of
these will actually be new configurations, i.e. requiring a process of
evaluation. Thus, number of total new simulations $N_{tot}$ 
can be estimated to be bounded as follows:
\[
K \le N_{tot} \le K \times E_{tot}
\]
where $E_{tot}$ is the nuber of eras executed and assuming that at
least $K$ evaluation should be performed in order to obtain the first
pareto $\mathscr{P}_0$.
